
%see https://tex.stackexchange.com/questions/25798/how-can-i-add-abstract-and-acknowledgement-pages-into-the-table-of-contents
\chapter*{Acknowledgments}%
\addcontentsline{toc}{chapter}{Acknowledgments}%

Obtaining a Ph.D.\ in Germany was 
one of the best things I~could dream of.
When I~finally got the chance to study in Germany,
I~was thrilled and I~wanted to do my best.
Now I~feel so proud of myself because I~have come this far.
Of course, this dissertation would not have been possible
if it were not for the help of many people.

First of all, I~would like to thank my first supervisor, 
Prof.\ Dr.\ Alexander ``Sascha'' Wolff.
I~am grateful to him for giving me 
the opportunity to pursue my Ph.D.\ in his group.
The research work was challenging,
but I~enjoyed working with him.
Sascha has been very patient with me.
When I~first came to Germany, I~could barely speak English.
He had to put a lot of effort into understanding me
when we were doing research.
Sascha advised me to take lectures and sent me to conferences
so that I~could learn as much as possible.
Sascha always encouraged me to ask questions
because I~can benefit from the answers.
He told me not to be shy even when 
I~fear that the questions are stupid;
other people in the audience may appreciate my asking
because they may have the same questions
but don't dare to ask.
%% Here, the point is not so clear (and not so exciting); I'd drop it.
% Sascha always responded my requests promptly.
% Once, I~noticed that I~was missing a letter from him 
% for some business on the next day
% while he was attending a conference in Italy.
% Nevertheless, after I~had written him an email,
% he sent me the letter before 20:00.
At some point,
Sascha even negotiated with my landlords 
when I~moved from an apartment into another.
Moreover, Sascha has a good sense of humor, 
and we often cracked jokes together.
I~was lucky to have him as my supervisor.

I~also thank my second supervisor, 
Prof.\ Dr.\ Jan-Henrik Haunert.  
In his lecture \emph{Algorithms for GIS}, 
he taught me many fundamentals of GIScience.  
Later, he moved to other universities 
and invited me to visit him there.
During the visits, we sketched many ideas together.
In particular, he proposed % the research of 
using the \Astar algorithm 
to find optimal sequences for area aggregation,
which led to the most important chapter of my dissertation.
Furthermore, he recommended many suitable conferences to me
when I~wanted to publish my papers.
% He taught me the ``optimization mantra'' (explain?).
% DP: I~do not understand ``optimization mantra''
% AW: A "mantra" is a sequence of words that are repeated over and
% over because they are so important:
% https://en.wikipedia.org/wiki/Mantra
% Mantras [....] helps to induce an altered state of consciousness.
% :-)

I~am grateful to all the colleagues in our group:
Moritz Beck, Johannes Blum, Benedikt Budig, 
Steven Chaplick, Thomas van Dijk, 
Martin Fink, Oksana Firman, Krzysztof Fleszar, 
Philipp Kindermann, Myroslav Kryven, 
Fabian Lipp, Andre L\"offler, 
Nadine Schwartges, Joachim Spoerhase, Sabine Storandt, 
and Johannes Zink.
%
We often had coffees together,
and it was a lot of fun to play squash and to go out for our excursions.
It was nice that our group always had lunch together
so that we had plenty of chances to learn from each other.
Indeed, I~sometimes took advantage of these lunches
to get suggestions regarding my research work.
%
I~am also grateful to Sigrid Keller.
She found an apartment for me 
before I~arrived in Germany.
Then, she picked me up at the train station of W\"urzburg
and brought me to that apartment.
She was very kind to me 
and helped me to fill many forms related to my Ph.D.\ study.


I~am indebted to Dr.\ Krzysztof Fleszar for 
helping me a lot during my Ph.D.\ study.
He is very warm-hearted.
Whenever he found that I~had problems to understand a paper,
he read that paper and then explained it to me.
He always helped when I~needed a German--English translator.
He helped me move twice using the van of his family.
On the day before my defense, he worked as hard as me
in order to give me feedback about my slides.
He has always invited me to join his parties, 
which brought me many great times.

I~thank Dr.\ Guillaume Touya for inviting me to visit
the French National Mapping Agency (IGN).
The visit was a great chance and gave me insight into
practical requirements regarding maps.
Our collaboration resulted in a paper on continuously
generalizing buildings into built-up areas.
%
I~also thank Dr.\ Thomas van Dijk.
He helped me speed up my 
least-squares adjustment using \emph{Eigen}, a C++ library.
He has proofread some of my papers
and has given me helpful suggestions 
concerning many aspects of my research.

I~am grateful to Prof.\ Dr.\ Min Deng,
the supervisor of my master's study.
He introduced me into the research area of 
continuous map generalization 
and helped me to get the chance of
pursuing my Ph.D.\ at the University of W\"urzburg.
Under his supervision,
we coauthored some nice papers.


I~thank Prof.\ Dr.\ Dirk Burghardt 
for reviewing my dissertation within a short time frame
when my working contract in W\"urzburg was about to end.
I~also thank him for introducing my research work to
Prof.\ Dr.\ Peter van Oosterom, 
which certainly helped me to get a postdoc position
in Peter's group.
Before submitting the final version of my dissertation,
I~have already been working in Peter's group.
I~would like to thank Peter and Dr.\ Martijn Meijers 
for allowing me to finish my paper about area aggregation,
which is part of this dissertation.

I~would like to thank my parents
for all their love and encouragement.
I~thank them for their suggestions 
when I~was making decisions.
%My special thanks go to Fang Wu.
%She has been very supportive of me.
%We enjoyed many activities together, 
%including hiking, skating, skiing, shopping, and so on.
%She made my life much more colorful.
I~thank all my friends in W\"urzburg
for their company.
Because of them, I~could better explore the city 
and even the whole country.

I~am very grateful to the University of W\"urzburg,
which is a treasure trove of knowledge. 
I~had the opportunity to take many courses.
In order to gain sufficient credits for 
obtaining a Ph.D.\ degree in Computer Science,
I~took some courses
(e.g., \emph{Theoretical Computer Science}
and \emph{Algorithms and Data Structures})
in my own faculty, 
the Faculty of Mathematics and Computer Science.
%
In order to improve my language skills,
I~took many courses
offered by the Language Center
(e.g., \emph{English for the Natural Sciences} 
and \emph{General Language Exercise of German})
and by the Faculty of Arts 
(e.g., \emph{Introduction to English Linguistics}).


The reviewers of my dissertation were
Prof.\ Dr.\ Alexander Wolff and Prof.\ Dr.\ Dirk Burghardt.
I defended my dissertation on December 21, 2017.
The defense examiners were Prof.\ Dr.\ Andreas N\"uchter (chair),
Prof.\ Dr.\ Jan-Henrik Haunert, and Prof.\ Dr.\ Alexander Wolff.


%\bigskip\noindent
%{
%\setlength{\tabcolsep}{0em}	
%\begin{tabular}{x{4cm}l}
%Supervisors:	    & ~Prof.\ Dr.\ Alexander Wolff\\
%					& ~Prof.\ Dr.\ Jan-Henrik Haunert
%					\vspace{4pt}\\ 
%Reviewers:			& ~Prof.\ Dr.\ Alexander Wolff\\
%					& ~Prof.\ Dr.\ Dirk Burghardt
%					\vspace{4pt}\\
%Defense Examiners:	& ~Prof.\ Dr.\ Andreas N\"uchter\\
%					& ~Prof.\ Dr.\ Jan-Henrik Haunert\\
%					& ~Prof.\ Dr.\ Alexander Wolff
%					\vspace{4pt}\\
%\multicolumn{2}{l}{Defended on December 21, 2017}					
%\end{tabular}
%}